\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}

### 2014-03-25 papers/jss/article.Rnw
minor pass over Murray's excellent edits
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@886 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\proglang{R} also does not support the native 64-bit integer type. Numeric vectors
with values $\geq 2^{31}$ can only be stored as doubles, which have
limited precision. Thereby \proglang{R} loses the ability to distinguish some
distinct integers:

@@

However, most modern languages do have support for 64-bit integers, 
which becomes problematic when \pkg{RProtoBuf} is used to exchange data 
with a system that requires this integer type. To work around this, 
\pkg{RProtoBuf} allows users to get and set 64-bit integer values by specifying 
them as character strings.

On 64-bit platforms, character strings representing large decimal
numbers will be coerced to int64 during assignment to 64-bit protocol
buffer types to work around the lack of native 64-bit types in \proglang{R}.  The
values are stored as distinct int64 values in memory but when accessed
from \proglang{R} language code they will be coerced into numeric values.  If the
full 64-bit precision is required, the \code{RProtoBuf.int64AsString}
option can be set to \code{TRUE} to return int64 values from messages as character
strings.  The character values are useful because they can
accurately be used as unique identifiers and can easily be passed to \proglang{R}
packages such as \pkg{int64} \citep{int64} or \pkg{bit64}
\citep{bit64} which represent 64-bit integers in \proglang{R}.

>>>>

\proglang{R} also does not support the native 64-bit integer type. Numeric vectors
with integer values greater or equal to $2^{31}$ can only be stored as
floating-point double precision variables. This conversion incurs a loss of
precision, and \proglang{R} loses the ability to distinguish between some
distinct integer variables:

@@

Most modern languages do have support for 64-bit integer values, 
which becomes problematic when \pkg{RProtoBuf} is used to exchange data 
with a system that requires this integer type. To work around this, 
\pkg{RProtoBuf} allows users to get and set 64-bit integer values by specifying 
them as character strings.

On 64-bit platforms, character strings representing large decimal
numbers will be coerced to \code{int64} during assignment to 64-bit Protocol
Buffer types to work around the lack of native 64-bit types in \proglang{R} itself.  The
values are stored as distinct \code{int64} values in memory. But when accessed
from \proglang{R} language code, they will be coerced into numeric
(floating-point) values.  If the
full 64-bit precision is required, the \code{RProtoBuf.int64AsString}
option can be set to \code{TRUE} to return \code{int64} values from messages as character
strings.  Such character values are useful because they can
accurately be used as unique identifiers, and can easily be passed to \proglang{R}
packages such as \pkg{int64} \citep{int64} or \pkg{bit64}
\citep{bit64} which represent 64-bit integers in \proglang{R}.
